EnVision CF Analyses

### 2025-07-09 Christine Chan/EnVision CF/envision_analyses.qmd
EnVision basic outline done

```{r}
# Timepoint and variables lists
timepoints <- c(0, 10, 30, 60, 90, 120, 150, 180)
limited_timepoints <- c(0, 120, 150, 180)
glucoses <- paste0("Glucose_", timepoints)
insulins <- paste0("Insulin_", timepoints)
cpeptides <- paste0("C.Peptide_", timepoints)
epinephrines <- paste0("Epinephrine_", timepoints)
norepinephrines <- paste0("Norepinephrine_", timepoints)
adren_survey <- paste0("adren_score_", limited_timepoints)
neuro_survey <- paste0("neuro_score_", limited_timepoints)
total_survey <- paste0("total_score_", limited_timepoints)
num_symptoms_survey <- paste0("num_symptoms_", limited_timepoints)
hypo_surveys <- c(adren_survey, neuro_survey, total_survey, num_symptoms_survey)
# First visit dataframe
first_visit_df <- final_df %>%
  group_by(study_id) %>%
  filter(row_number() == 1) %>%
  ungroup()
# Long data for mixed models
glmm_df <- final_df %>%
  select(
    study_id, Hypo60, Hypo70, ogtt_num,
    all_of(c(
      glucoses, insulins, cpeptides, epinephrines, norepinephrines,
      hypo_surveys
    ))
  ) %>%
  pivot_longer(
    all_of(c(
      glucoses, insulins, cpeptides, epinephrines, norepinephrines,
      hypo_surveys
    )),
    names_to = c(".value", "Timepoint"),
    names_pattern = "(.*)_([0-9]{1,3})"
  )
glmm_df$Timepoint <- factor(glmm_df$Timepoint, levels = timepoints)
```

@@

@@

Glucose was modeled using a linear mixed effect model with random intercept for participant and time treated as a categorical variable. The results from this model are presented as estimated marginal means (also known as least-squares means) for those with hypoglycemia at some point and those with no hypoglycemia.

@@

Insulin was modeled using a linear mixed effect model with random intercept for participant and time treated as a categorical variable. The results from this model are presented as estimated marginal means (also known as least-squares means) for those with hypoglycemia at some point and those with no hypoglycemia.

@@

C-peptide was modeled using a linear mixed effect model with random intercept for participant and time treated as a categorical variable. The results from this model are presented as estimated marginal means (also known as least-squares means) for those with hypoglycemia at some point and those with no hypoglycemia.

@@

## Whole OGTT Measures

>>>>

```{r}
# Timepoint and variables lists
timepoints <- c(0, 10, 30, 60, 90, 120, 150, 180)
limited_timepoints <- c(0, 120, 150, 180)
glucoses <- paste0("Glucose_", timepoints)
insulins <- paste0("Insulin_", timepoints)
cpeptides <- paste0("C.Peptide_", timepoints)
glucagons <- paste0("Glucagon_", timepoints)
glp1s <- paste0("GLP.1.Active_", timepoints)
gips <- paste0("GIP_", timepoints)
epinephrines <- paste0("Epinephrine_", timepoints)
norepinephrines <- paste0("Norepinephrine_", timepoints)
adren_survey <- paste0("adren_score_", limited_timepoints)
neuro_survey <- paste0("neuro_score_", limited_timepoints)
total_survey <- paste0("total_score_", limited_timepoints)
num_symptoms_survey <- paste0("num_symptoms_", limited_timepoints)
hypo_surveys <- c(adren_survey, neuro_survey, total_survey, num_symptoms_survey)
# First visit dataframe
first_visit_df <- final_df %>%
  group_by(study_id) %>%
  filter(row_number() == 1) %>%
  ungroup()
# Long data for mixed models
glmm_df <- final_df %>%
  select(
    study_id, Hypo60, Hypo70, ogtt_num,
    all_of(c(
      glucoses, insulins, cpeptides, glucagons, glp1s, gips, epinephrines,
      norepinephrines, hypo_surveys
    ))
  ) %>%
  pivot_longer(
    all_of(c(
      glucoses, insulins, cpeptides, glucagons, glp1s, gips, epinephrines,
      norepinephrines, hypo_surveys
    )),
    names_to = c(".value", "Timepoint"),
    names_pattern = "(.*)_([0-9]{1,3})"
  )
glmm_df$Timepoint <- factor(glmm_df$Timepoint, levels = timepoints)
```

@@

Glucose, insulin, C-peptide, glucagon, epinephrine, and norepinephrine were modeled using a linear mixed effect model with random effects for OGTT within participant and time treated as a categorical variable. The results from this model are presented as estimated marginal means (also known as least-squares means) for those with hypoglycemia at some point and those with no hypoglycemia.

@@

@@

@@

@@

### Glucagon

```{r}
# Fit
mod <- lmer(Glucagon ~ Timepoint * Hypo70 + (1 | study_id / ogtt_num),
  data = glmm_df
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo70"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo70", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo70,
  group = Hypo70
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean Glucagon") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

The table above shows the estimated mean glucagon at each time point for the two groups. For example, for those with no hypoglycemia the mean two hour glucagon was `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","CI Upper Limit"],2)`) and for those with hypoglycemia at some point the mean two hour glucagon was `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","CI Upper Limit"],2)`).

```{r}
# Fit
mod <- lmer(Glucagon ~ Timepoint * Hypo60 + (1 | study_id / ogtt_num),
  data = glmm_df
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo60"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo60", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo60,
  group = Hypo60
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean Glucagon") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

The table above shows the estimated mean glucagon at each time point for the two groups. For example, for those with no hypoglycemia the mean two hour glucagon was `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","CI Upper Limit"],2)`) and for those with hypoglycemia at some point the mean two hour glucagon was `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","CI Upper Limit"],2)`).

### GLP-1

```{r}
# Fit
mod <- lmer(GLP.1.Active ~ Timepoint * Hypo70 + (1 | study_id / ogtt_num),
  data = glmm_df
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo70"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo70", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo70,
  group = Hypo70
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean GLP-1") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

The table above shows the estimated mean GLP-1 at each time point for the two groups. For example, for those with no hypoglycemia the mean two hour GLP-1 was `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","CI Upper Limit"],2)`) and for those with hypoglycemia at some point the mean two hour GLP-1 was `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","CI Upper Limit"],2)`).

```{r}
# Fit
mod <- lmer(GLP.1.Active ~ Timepoint * Hypo60 + (1 | study_id / ogtt_num),
  data = glmm_df
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo60"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo60", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo60,
  group = Hypo60
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean GLP-1") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

The table above shows the estimated mean GLP-1 at each time point for the two groups. For example, for those with no hypoglycemia the mean two hour GLP-1 was `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","CI Upper Limit"],2)`) and for those with hypoglycemia at some point the mean two hour GLP-1 was `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","CI Upper Limit"],2)`).

### GIP

```{r}
# Fit
mod <- lmer(GIP ~ Timepoint * Hypo70 + (1 | study_id / ogtt_num),
  data = glmm_df
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo70"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo70", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo70,
  group = Hypo70
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean GIP") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

The table above shows the estimated mean GIP at each time point for the two groups. For example, for those with no hypoglycemia the mean two hour GIP was `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","CI Upper Limit"],2)`) and for those with hypoglycemia at some point the mean two hour GIP was `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","CI Upper Limit"],2)`).

```{r}
# Fit
mod <- lmer(GIP ~ Timepoint * Hypo60 + (1 | study_id / ogtt_num),
  data = glmm_df
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo60"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo60", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo60,
  group = Hypo60
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean GIP") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

The table above shows the estimated mean GIP at each time point for the two groups. For example, for those with no hypoglycemia the mean two hour GIP was `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","CI Upper Limit"],2)`) and for those with hypoglycemia at some point the mean two hour GIP was `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","CI Upper Limit"],2)`).

### Epinephrine

```{r}
# Fit
mod <- lmer(Epinephrine ~ Timepoint * Hypo70 + (1 | study_id / ogtt_num),
  data = glmm_df
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo70"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo70", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo70,
  group = Hypo70
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean Epinephrine") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

The table above shows the estimated mean epinephrine at each time point for the two groups. For example, for those with no hypoglycemia the mean two hour epinephrine was `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","CI Upper Limit"],2)`) and for those with hypoglycemia at some point the mean two hour epinephrine was `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","CI Upper Limit"],2)`).

```{r}
# Fit
mod <- lmer(Epinephrine ~ Timepoint * Hypo60 + (1 | study_id / ogtt_num),
  data = glmm_df
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo60"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo60", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo60,
  group = Hypo60
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean Epinephrine") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

The table above shows the estimated mean epinephrine at each time point for the two groups. For example, for those with no hypoglycemia the mean two hour epinephrine was `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","CI Upper Limit"],2)`) and for those with hypoglycemia at some point the mean two hour epinephrine was `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","CI Upper Limit"],2)`).

### Norepinephrine

```{r}
# Fit
mod <- lmer(Norepinephrine ~ Timepoint * Hypo70 + (1 | study_id / ogtt_num),
  data = glmm_df
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo70"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo70", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo70,
  group = Hypo70
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean Norepinephrine") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

The table above shows the estimated mean norepinephrine at each time point for the two groups. For example, for those with no hypoglycemia the mean two hour norepinephrine was `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","CI Upper Limit"],2)`) and for those with hypoglycemia at some point the mean two hour norepinephrine was `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","CI Upper Limit"],2)`).

```{r}
# Fit
mod <- lmer(Norepinephrine ~ Timepoint * Hypo60 + (1 | study_id / ogtt_num),
  data = glmm_df
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo60"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo60", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo60,
  group = Hypo60
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean Norepinephrine") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

The table above shows the estimated mean norepinephrine at each time point for the two groups. For example, for those with no hypoglycemia the mean two hour norepinephrine was `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","CI Upper Limit"],2)`) and for those with hypoglycemia at some point the mean two hour norepinephrine was `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","CI Upper Limit"],2)`).

### `adren_score`

The `adren_score` variable was modeled using a mixed effect Poisson model with random effects for OGTT within participant and time treated as a categorical variable.

```{r}
# Fit
# Poisson model better than NB by AIC and BIC
mod <- glmer(adren_score ~ Timepoint * Hypo70 + (1 | study_id / ogtt_num),
  data = glmm_df, family = "poisson",
  control = glmerControl(optimizer = "bobyqa")
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo70"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo70", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo70,
  group = Hypo70
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean adren_score") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

The table above shows the estimated mean norepinephrine at each time point for the two groups. For example, for those with no hypoglycemia the mean two hour norepinephrine was `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","CI Upper Limit"],2)`) and for those with hypoglycemia at some point the mean two hour norepinephrine was `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","CI Upper Limit"],2)`).

```{r}
# Fit
# Poisson model better than NB by AIC and BIC
mod <- glmer(adren_score ~ Timepoint * Hypo60 + (1 | study_id / ogtt_num),
  data = glmm_df, family = "poisson",
  control = glmerControl(optimizer = "bobyqa")
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo60"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo60", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo60,
  group = Hypo60
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean adren_score") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

The table above shows the estimated mean norepinephrine at each time point for the two groups. For example, for those with no hypoglycemia the mean two hour norepinephrine was `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","CI Upper Limit"],2)`) and for those with hypoglycemia at some point the mean two hour norepinephrine was `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","CI Upper Limit"],2)`).

### `neuro_score`

The `neuro_score` variable was modeled using a mixed effect Poisson model with random effects for OGTT within participant and time treated as a categorical variable.

```{r}
# Fit
# Poisson model better than NB by AIC and BIC
mod <- glmer(neuro_score ~ Timepoint * Hypo70 + (1 | study_id / ogtt_num),
  data = glmm_df, family = "poisson",
  control = glmerControl(optimizer = "bobyqa")
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo70"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo70", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo70,
  group = Hypo70
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean neuro_score") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

The table above shows the estimated mean norepinephrine at each time point for the two groups. For example, for those with no hypoglycemia the mean two hour norepinephrine was `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","CI Upper Limit"],2)`) and for those with hypoglycemia at some point the mean two hour norepinephrine was `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","CI Upper Limit"],2)`).

```{r}
# Fit
# Poisson model better than NB by AIC and BIC
mod <- glmer(neuro_score ~ Timepoint * Hypo60 + (1 | study_id / ogtt_num),
  data = glmm_df, family = "poisson",
  control = glmerControl(optimizer = "bobyqa")
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo60"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo60", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo60,
  group = Hypo60
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean neuro_score") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

The table above shows the estimated mean norepinephrine at each time point for the two groups. For example, for those with no hypoglycemia the mean two hour norepinephrine was `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo60=="No Hypoglycemia < 60" & means$Timepoint=="120","CI Upper Limit"],2)`) and for those with hypoglycemia at some point the mean two hour norepinephrine was `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo60=="Hypoglycemia < 60" & means$Timepoint=="120","CI Upper Limit"],2)`).

### `total_score`

The `total_score` variable was modeled using a mixed effect Poisson model with random effects for OGTT within participant and time treated as a categorical variable.

```{r}
# Fit
# Poisson model better than NB by AIC and BIC
mod <- glmer(total_score ~ Timepoint * Hypo70 + (1 | study_id / ogtt_num),
  data = glmm_df, family = "poisson",
  control = glmerControl(optimizer = "bobyqa")
)
# EM means
means <- data.frame(emmeans(mod, c("Timepoint", "Hypo70"),
  type = "response",
  pbkrtest.limit = 1e6
))
colnames(means) <- c(
  "Timepoint", "Hypo70", "Mean", "SE", "df", "CI Lower Limit", "CI Upper Limit"
)
# Plot
ggplot(means, aes(
  x = as.numeric(as.character(Timepoint)), y = Mean, colour = Hypo70,
  group = Hypo70
)) +
  geom_point() +
  geom_errorbar(aes(ymin = `CI Lower Limit`, ymax = `CI Upper Limit`),
    width = 3
  ) +
  geom_line() +
  scale_x_continuous(breaks = timepoints) +
  scale_color_manual(values = c("#66C2A5", "#FC8D62")) +
  ylab("EM Mean total_score") +
  xlab("Timepoint") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank())
```

The table above shows the estimated mean norepinephrine at each time point for the two groups. For example, for those with no hypoglycemia the mean two hour norepinephrine was `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo70=="No Hypoglycemia < 70" & means$Timepoint=="120","CI Upper Limit"],2)`) and for those with hypoglycemia at some point the mean two hour norepinephrine was `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","Mean"],2)` (95% CI: `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","CI Lower Limit"],2)` - `r round(means[means$Hypo70=="Hypoglycemia < 70" & means$Timepoint=="120","CI Upper Limit"],2)`).
